Worflow

### 2017-06-11 R/workflow.Rmd
biocparallel ncores

```{r}
fn <- '../data/zinb_batch.rda'
if (runZinb & !file.exists(fn)){
  mod <- model.matrix( ~ batch)
  print(system.time(zinb <- zinbDimRed(se, K = 50, X = mod, residuals = T,
                                       normalizedValues = T)))
  save(zinb, file = fn)
}else{
  load(fn)
}
```

>>>>

```{r}
fn <- '../data/zinb_batch.rda'
if (runZinb & !file.exists(fn)){
  mod <- model.matrix( ~ batch)
  print(system.time(zinb <- zinbDimRed(se, K = 50, X = mod, residuals = T,
                                       normalizedValues = T,
                                       BPPARAM = MulticoreParam(NCORES))))
  save(zinb, file = fn)
}else{
  load(fn)
}
```
